API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
Cosmit.

In other places of the library, in particular in the vectorization code
for unstructured input, the toolkit is also designed to be
extensible. Here, estimators provide hooks for user-defined code: objects or
functions that provide a specific API can be given as arguments at vectorizer
construction time. The library then calls into this code, communicating with it by passing objects of standard Python/NumPy types.
Again, such external user code can be kept agnostic of the \sklearn
class hierarchy.

>>>>

In other places of the library, in particular in the vectorization code
for unstructured input, the toolkit is also designed to be
extensible. Here, estimators provide hooks for user-defined code: objects or
functions that follow a specific API can be given as arguments at vectorizer
construction time. The library then calls into this code, communicating with it by passing objects of standard Python/NumPy types.
Again, such external user code can be kept agnostic of the \sklearn
class hierarchy.
